AggregateCounts

### 2021-06-25 R/AggregateCounts.Rmd
Added functions for plotting basica aggregates distributions for all the strains

```{r setup, include=FALSE}
library(conflicted)
library(tidyverse)
library(plotrix)#for std error
library(dplyr)
library(cowplot)
filter <- dplyr::filter
source("~/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/PaSaChronicWounds/R/readTiff.R")
library(EBImage) #for rtiff

aggregateList<-GetAggregates()#this reads the data from Matlab
# mutate(Strain = recode(Position, "0" = "Pa14 wt", "1"= "Pa14 -PA1414","2" = "Pa14 wt", "3"= "Pa14 -PA1414")) #this is to change the names

#agregate input functions
#####
ReadAggregateFile<-function(file, species, timepoint, condition, replicate){#make a dataframe of the aggregate size list and add experimental parameters 
   datos <-read.csv(file, header = F)  
   colnames(datos)<-c('Size') 
   datos<-datos %>% filter(!Size<0.5) #first filter the size
   datos<-datos %>% mutate(Species = species)#add parameters
   datos<-datos %>% mutate(TimePoint = timepoint) 
   datos<-datos %>% mutate(Condition = condition)
   datos<-datos %>% mutate(Replicate = replicate)
   datos$Species<-as.factor(datos$Species)
   datos$Replicate<-as.factor(datos$Replicate)
   datos$Condition<-as.factor(datos$Condition)
   datos$TimePoint<-as.factor(datos$TimePoint)
   return(datos)
}

GetAggregates<-function(){#import all experiments at once
   folder<- paste0('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Aggregate lists')
   fileList<-list.files(path = folder, full.names = TRUE)
   growthDf<-data.frame()
   for (aggList in 1:length(fileList)){
     fileName<-str_split(basename(fileList[aggList]), "\\.")[[1]][1]#this selects the base file name and removes the ".csv"
     attrList<-str_split(fileName,"_")[[1]]
     growthDf<-rbind(growthDf,ReadAggregateFile(fileList[aggList],attrList[4],attrList[2],attrList[1],attrList[3]))
     }
   return(growthDf)
}
#####
```
```{r aggregate wrangling}
#Statistics from all aggregates

#Get aggregate summary per sample
aggregateListSummaryReplicate<-aggregateList %>% group_by(Species, TimePoint, Condition, Replicate) %>% 
  summarise(Aggs = n(), biomass = sum(Size), meanAggSize = mean(Size), seAggSize = std.error(Size), maxSize = max(Size), minSize = min(Size)) %>%
  ungroup() %>% mutate(RatioMaxTotal = maxSize/biomass )

#Plot agg summary per sample
#####
ggplot()+
  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= meanAggSize, color = Species,shape = "MeanSize"),size = 3, height = 0, width = .1)+
  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= maxSize, color = Species, shape = "MaxSize"),size = 3, height = 0, width = .1)+
  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= biomass, color = Species, shape = "TotalBiomass"),size = 3, height = 0, width = .1)+  
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  facet_grid(. ~ Condition, scales = "free", space = "free") +
  ggtitle('Mean size and largest aggregate and total biomass per sample')+
  labs(x = "",y = "um3")+
  scale_shape_manual(name="Metric",values=c(MeanSize=1, MaxSize=2, TotalBiomass=17))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))
#####

#Get aggregate Summary per condition
aggregateListSummary<-aggregateList %>% group_by(Species, TimePoint, Condition) %>% 
  summarise(Aggs = n(), biomass = sum(Size), meanAggSize = mean(Size), seAggSize = std.error(Size), maxSize = max(Size), minSize = min(Size)) %>%
  ungroup() %>% mutate(RatioMaxTotal = maxSize/biomass ) 
#plot agg summary per condition
#####
ggplot()+
  geom_jitter(data = aggregateListSummary, aes(x = TimePoint, y= meanAggSize, color = Species,shape = "MeanSize"),size = 3, height = 0, width = .1)+
  geom_jitter(data = aggregateListSummary, aes(x = TimePoint, y= maxSize, color = Species, shape = "MaxSize"),size = 3, height = 0, width = .1)+
  geom_jitter(data = aggregateListSummary, aes(x = TimePoint, y= biomass, color = Species, shape = "TotalBiomass"),size = 3, height = 0, width = .1)+  
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  facet_grid(. ~ Condition, scales = "free", space = "free") +
  ggtitle('Mean size and largest aggregate and total biomass per sample')+
  labs(x = "",y = "um3")+
  scale_shape_manual(name="Metric",values=c(MeanSize=1, MaxSize=2, TotalBiomass=17))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))
#####
```
```{r non-fancy histogram}
#histogram<- hist(aggregateList$Size, breaks = c(0, 5, 10, 100, 1000, 10^9))#this is a simple way to do a histogram

#this pipe essentially gets to the producto of what fancy histograms do but more efficiently
#First including all sizes
#####
newHistogram.df<-aggregateList %>% mutate(LogBin = case_when(Size <= 5 ~ 5,
                        Size<= 10 ~ 10,
                        Size<= 100    ~ 100,
                        Size<= 1000   ~ 1000,
                        Size<= 10000  ~ 10000,
                        Size<= 100000 ~ 100000,
                        Size > 100000 ~ 1000000)) %>% group_by(Species,Condition,TimePoint, Replicate)%>% 
  mutate(TotalBiomass = sum(Size), TotalFrequency = n()) %>% ungroup() %>% group_by(Species,Condition,TimePoint, Replicate, LogBin)%>%
  mutate(BinBiomass = sum(Size), BinFrequency = n()) %>% ungroup() %>%
  mutate(NormalizedFrequency = BinFrequency/TotalFrequency*100, NormalizedBiomass = BinBiomass/TotalBiomass*100)

#This is weird, but I want to have the histogram above with all the data, and the one below with only the bins
newHistogramSummary.df<-newHistogram.df %>% group_by(Species,Condition,TimePoint, Replicate, LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Condition,TimePoint, Replicate) %>% mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))

#Plot Normalized Frequency
ggplot()+
    geom_jitter(data = newHistogramSummary.df,aes(x=as.factor(LogBin),y=NormalizedFrequency,  color =Species, ),size=3, height = 0, width = .2)+
    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
    facet_grid(.~TimePoint)+
    labs(y = "Normalized Frequency (%)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
#Plot Normalized Biomass
ggplot()+
    geom_jitter(data = newHistogramSummary.df,aes(x=as.factor(LogBin),y=NormalizedBiomass,  color =Species, ),size=3, height = 0, width = .2)+
    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
    facet_grid(.~TimePoint)+
    labs(y = "Normalized Biomass (%)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))

#Plot normalized Biomass per sample
ggplot()+
    geom_line(data = newHistogramSummary.df,aes(x=as.factor(LogBin),y=NormalizedBiomass, color = Replicate, group = Replicate ),size=1)+
    #scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
    guides(color = FALSE)+
    facet_grid(TimePoint~Species)+
    labs(y = "Normalized Biomass",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    theme_cowplot()+
    scale_colour_grey()+
    theme(plot.title = element_text(hjust = 0.5)) 
#####
#now only aggregates 5 microns or larger
#####
aggsOnlyHist.df<-aggregateList %>% mutate(LogBin = case_when(Size <= 5 ~ 5,
                        Size<= 10 ~ 10,
                        Size<= 100    ~ 100,
                        Size<= 1000   ~ 1000,
                        Size<= 10000  ~ 10000,
                        Size<= 100000 ~ 100000,
                        Size > 100000 ~ 1000000)) %>% filter(!LogBin == 5) %>% group_by(Species,Condition,TimePoint, Replicate)%>% 
  mutate(TotalBiomass = sum(Size), TotalFrequency = n()) %>% ungroup() %>% group_by(Species,Condition,TimePoint, Replicate, LogBin)%>%
  mutate(BinBiomass = sum(Size), BinFrequency = n()) %>% ungroup() %>%
  mutate(NormalizedFrequency = BinFrequency/TotalFrequency*100, NormalizedBiomass = BinBiomass/TotalBiomass*100)

#This is weird, but I want to have the histogram above with all the data, and the one below with only the bins
aggsOnlyHistSummary.df<-aggsOnlyHist.df %>% group_by(Species,Condition,TimePoint, Replicate, LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Condition,TimePoint, Replicate) %>% mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))

#now plot it
#normalized frequency
ggplot()+
    geom_jitter(data = aggsOnlyHistSummary.df,aes(x=as.factor(LogBin),y=NormalizedFrequency,  color =Species, ),size=3, height = 0, width = .2)+
    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
    facet_grid(.~TimePoint)+
    labs(y = "Normalized Frequency (%)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5)) 
#Normalized Biomass facet timepoint, color species
ggplot()+
    geom_jitter(data = aggsOnlyHistSummary.df,aes(x=as.factor(LogBin),y=NormalizedBiomass,  color =Species, ),size=3, height = 0, width = .2)+
    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
    facet_grid(.~TimePoint)+
    labs(y = "Normalized Biomass (%)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5)) 
#Normalized Biomass facet species, color timepoint
ggplot()+
    geom_jitter(data = aggsOnlyHistSummary.df,aes(x=as.factor(LogBin),y=NormalizedBiomass,  color =TimePoint, ),size=3, height = 0, width = .2)+
    #scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
    facet_grid(.~Species)+
    labs(y = "Normalized Biomass",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5)) 
#Normalized Biomass facet species and Timepoint, color Replicate
ggplot()+
    geom_line(data = aggsOnlyHistSummary.df,aes(x=as.factor(LogBin),y=NormalizedBiomass, color = Replicate, group = Replicate ),size=1)+
    #scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
    guides(color = FALSE)+
    facet_grid(TimePoint~Species)+
    labs(y = "Normalized Biomass",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    theme_cowplot()+
    scale_colour_grey()+
    theme(plot.title = element_text(hjust = 0.5))

#####
#Planktonic vs aggregates
#####
#Add agregation value to the dataframe
newHistogram.df<-newHistogram.df %>%  mutate(Aggregation = case_when(LogBin == 5 ~ "Planktonic",LogBin>5 ~ "Aggregate")) %>%
  group_by(Species,Condition,TimePoint, Replicate, Aggregation)%>% 
  mutate(AgPlBiomass = sum(Size), AgPlFreq = n()) %>% ungroup() %>%
  mutate(AgPlNormFrequency = AgPlFreq/TotalFrequency*100, AgPlNormBiomass = AgPlBiomass/TotalBiomass*100)
#Collapse to only values per replicate
plankAggHist<-newHistogram.df %>% group_by(Species,Condition,TimePoint, Replicate, Aggregation,AgPlNormFrequency,AgPlNormBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Condition,TimePoint, Replicate) %>% mutate(checkAggFreq =sum(AgPlNormFrequency), checkAggBiomass = sum(AgPlNormBiomass))
#plot Frequency
ggplot()+
    geom_jitter(data = plankAggHist,aes(x=as.factor(Aggregation),y=AgPlNormFrequency,  color =Species, ),size=3, height = 0, width = .2)+ 
    #scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
    facet_grid(.~TimePoint)+
    labs(y = "Normalized Frequency (%)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5)) 
#Plot Biomass
ggplot()+
    geom_jitter(data = plankAggHist,aes(x=as.factor(Aggregation),y=AgPlNormBiomass,  color =Species, ),size=3, height = 0, width = .2)+
    #scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
    facet_grid(.~TimePoint)+
    labs(y = "Normalized Biomass (%)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5)) 
#####
```

>>>>

```{r setup, include=FALSE}
library(conflicted)
library(tidyverse)
library(plotrix)#for std error
library(dplyr)
library(cowplot)
filter <- dplyr::filter
source("~/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/PaSaChronicWounds/R/readTiff.R")
library(EBImage) #for rtiff
```

```{r aggregate input}
aggregateList<-GetAggregates()#this reads the data from Matlab
# mutate(Strain = recode(Position, "0" = "Pa14 wt", "1"= "Pa14 -PA1414","2" = "Pa14 wt", "3"= "Pa14 -PA1414")) #this is to change the names
removable <- aggregateList %>% filter(Species == "Pa" & Condition == "mono")
aggregateList <- anti_join(aggregateList, removable)

#agregate input functions
#####
ReadAggregateFile<-function(file, species, timepoint, condition, replicate){#make a dataframe of the aggregate size list and add experimental parameters
  print(file)
   datos <-read.csv(file, header = F)  
   colnames(datos)<-c('Size') 
   datos<-datos %>% filter(!Size<0.5) #first filter the size
   datos<-datos %>% mutate(Species = species)#add parameters
   datos<-datos %>% mutate(TimePoint = timepoint) 
   datos<-datos %>% mutate(Condition = condition)
   datos<-datos %>% mutate(Replicate = replicate)
   datos$Species<-as.factor(datos$Species)
   datos$Replicate<-as.factor(datos$Replicate)
   datos$Condition<-as.factor(datos$Condition)
   datos$TimePoint<-as.factor(datos$TimePoint)
   return(datos)
}

GetAggregates<-function(){#import all experiments at once
   folder<- paste0('/Volumes/raw_data/Confocal/Carolyn/2020/Chronic wounds/Aggregate lists')
   fileList<-list.files(path = folder, full.names = TRUE)
   growthDf<-data.frame()
   for (aggList in 1:length(fileList)){
     fileName<-str_split(basename(fileList[aggList]), "\\.")[[1]][1]#this selects the base file name and removes the ".csv"
     attrList<-str_split(fileName,"_")[[1]]
     growthDf<-rbind(growthDf,ReadAggregateFile(fileList[aggList],attrList[4],attrList[2],attrList[1],attrList[3]))
     }
   return(growthDf)
}
#####
```
```{r aggregate wrangling and overview plots}
#Statistics from all aggregates

#Get aggregate summary per sample
aggregateListSummaryReplicate<-aggregateList%>% group_by(Species, TimePoint, Condition, Replicate) %>% 
  summarise(Aggs = n(), biomass = sum(Size), meanAggSize = mean(Size), seAggSize = std.error(Size), maxSize = max(Size), minSize = min(Size)) %>%
  ungroup() %>% mutate(RatioMaxTotal = maxSize/biomass )

#Plot agg summary per sample
#####
ggplot()+ 
  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= meanAggSize, color = Species,shape = "MeanSize"),size = 3, height = 0, width = .1)+
  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= maxSize, color = Species, shape = "MaxSize"),size = 3, height = 0, width = .1)+
  geom_jitter(data = aggregateListSummaryReplicate, aes(x = TimePoint, y= biomass, color = Species, shape = "TotalBiomass"),size = 3, height = 0, width = .1)+  
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  facet_grid(. ~ Condition, scales = "free", space = "free") +
  ggtitle('Mean size and largest aggregate and total biomass per sample')+
  labs(x = "",y = bquote(paste("Volume (", mu*"m"^3*")")))+
  scale_shape_manual(name="Metric",values=c(MeanSize=1, MaxSize=2, TotalBiomass=17))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))
#####

#Get aggregate Summary per condition
aggregateListSummary<-aggregateList %>% group_by(Species, TimePoint, Condition) %>% 
  summarise(Aggs = n(), biomass = sum(Size), meanAggSize = mean(Size), seAggSize = std.error(Size), maxSize = max(Size), minSize = min(Size)) %>%
  ungroup() %>% mutate(RatioMaxTotal = maxSize/biomass ) 
#plot agg summary per condition
#####
ggplot()+
  geom_jitter(data = aggregateListSummary, aes(x = TimePoint, y= meanAggSize, color = Species,shape = "MeanSize"),size = 3, height = 0, width = .1)+
  geom_jitter(data = aggregateListSummary, aes(x = TimePoint, y= maxSize, color = Species, shape = "MaxSize"),size = 3, height = 0, width = .1)+
  geom_jitter(data = aggregateListSummary, aes(x = TimePoint, y= biomass, color = Species, shape = "TotalBiomass"),size = 3, height = 0, width = .1)+ 
  scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  facet_grid(. ~ Condition, scales = "free", space = "free") +
  ggtitle('Mean size and largest aggregate and total biomass per sample')+
  labs(x = "",y = bquote(paste("Volume (", mu*"m"^3*")")))+
  scale_shape_manual(name="Metric",values=c(MeanSize=1, MaxSize=2, TotalBiomass=17))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5))
#####
```
```{r non-fancy histogram}
#histogram<- hist(aggregateList$Size, breaks = c(0, 5, 10, 100, 1000, 10^9))#this is a simple way to do a histogram

#this pipe essentially gets to the product of what fancy histograms do but more efficiently
#First including all sizes
#####

#There are two ways to normalize the Bin Frequncy and Bin Biomass, per condition and per sample, so I'll do both
#First per replicate:
HistReplicate<-aggregateList %>% mutate(LogBin = case_when(Size <= 5 ~ 5,
                        Size<= 10 ~ 10,
                        Size<= 100    ~ 100,
                        Size<= 1000   ~ 1000,
                        Size<= 10000  ~ 10000,
                        Size<= 100000 ~ 100000,
                        Size > 100000 ~ 1000000)) %>% group_by(Species,Condition,TimePoint, Replicate)%>% 
  mutate(TotalBiomass = sum(Size), TotalFrequency = n()) %>% ungroup() %>% group_by(Species,Condition,TimePoint, Replicate, LogBin)%>%
  mutate(BinBiomass = sum(Size), BinFrequency = n()) %>% ungroup() %>%
  mutate(NormalizedFrequency = BinFrequency/TotalFrequency*100, NormalizedBiomass = BinBiomass/TotalBiomass*100)

#This is weird, but I want to have the histogram above with all the data, and the one below with only the bins
HistReplicateSummary<-HistReplicate %>% group_by(Species,Condition,TimePoint, Replicate, LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Condition,TimePoint, Replicate) %>% mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))

#Now per condition. The difference is int the "group_by" part
HistCondition<-aggregateList %>% mutate(LogBin = case_when(Size <= 5 ~ 5,
                        Size<= 10 ~ 10,
                        Size<= 100    ~ 100,
                        Size<= 1000   ~ 1000,
                        Size<= 10000  ~ 10000,
                        Size<= 100000 ~ 100000,
                        Size > 100000 ~ 1000000)) %>% group_by(Species,Condition,TimePoint)%>% 
  mutate(TotalBiomass = sum(Size), TotalFrequency = n()) %>% ungroup() %>%
  group_by(Species,Condition,TimePoint,LogBin)%>%
  mutate(BinBiomass = sum(Size), BinFrequency = n()) %>% ungroup() %>%
  mutate(NormalizedFrequency = BinFrequency/TotalFrequency*100, NormalizedBiomass = BinBiomass/TotalBiomass*100)

#Summary data frame
HistConditionSummary<-HistCondition %>%
  group_by(Species,Condition,TimePoint,LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>% 
  unique()%>%ungroup() %>%  group_by(Species,Condition,TimePoint) %>% 
  mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))

#Plot Normalized Frequency
#this isn't useful as the normalized Frequency changes with replicate, so it's better to pool all samples together
PlotHistSum<-function(rep.df,cond.df, y_var, title){
ggplot()+
    geom_jitter(data = HistReplicateSummary,aes(x=as.factor(LogBin),y=.data[[y_var]],  color =Species ),size=3, height = 0, width = .2, shape = 1)+
    geom_point(data = HistConditionSummary,aes(x=as.factor(LogBin),y=.data[[y_var]],  color =Species,group = Species),size=4, shape = 16, position = position_dodge(width = .3) )+
    scale_y_log10(breaks = c(100, 10, 1, .1, .01), labels = c(100, 10, 1, .1, .01))+
    facet_grid(Condition~TimePoint)+
    ggtitle(title)+
    labs(y = paste(y_var,"(%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
}

PlotHistSum(HistReplicateSummary,HistConditionSummary,"NormalizedFrequency", "Normalized Frequency all sizes")

PlotHistSum(HistReplicateSummary,HistConditionSummary,"NormalizedBiomass", "Normalized Biomass all sizes")

#Plot normalized Biomass per sample
##Pa
PlotHistRepBioTrend<-function(rep.df,species){
ggplot()+
    geom_line(data = rep.df %>% filter(Species==species),aes(x=as.factor(LogBin),y=NormalizedBiomass, color = Replicate, group = Replicate ),size=1)+
    guides(color = FALSE)+
    facet_grid(Condition~TimePoint)+
    labs(y = "Normalized Biomass",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
    ggtitle(paste('Normalized Biomass per Sample', species))+
    theme_cowplot()+
    scale_colour_grey()+
    theme(plot.title = element_text(hjust = 0.5)) }
PlotHistRepBioTrend(HistReplicateSummary, "Pa")
PlotHistRepBioTrend(HistReplicateSummary, "Sa")

#####
#now only aggregates 5 microns or larger
#####
#Separating the replicates
aggsHistRep<-aggregateList %>% mutate(LogBin = case_when(Size <= 5 ~ 5,
                        Size<= 10 ~ 10,
                        Size<= 100    ~ 100,
                        Size<= 1000   ~ 1000,
                        Size<= 10000  ~ 10000,
                        Size<= 100000 ~ 100000,
                        Size > 100000 ~ 1000000)) %>% filter(!LogBin == 5) %>% group_by(Species,Condition,TimePoint, Replicate)%>% 
  mutate(TotalBiomass = sum(Size), TotalFrequency = n()) %>% ungroup() %>% group_by(Species,Condition,TimePoint, Replicate, LogBin)%>%
  mutate(BinBiomass = sum(Size), BinFrequency = n()) %>% ungroup() %>%
  mutate(NormalizedFrequency = BinFrequency/TotalFrequency*100, NormalizedBiomass = BinBiomass/TotalBiomass*100)

##Summary df
aggsHistRepSum<-aggsHistRep %>% group_by(Species,Condition,TimePoint, Replicate, LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Condition,TimePoint, Replicate) %>% mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))

#Pooling replicates together
aggsHistCond<-aggregateList %>% mutate(LogBin = case_when(Size <= 5 ~ 5,
                        Size<= 10 ~ 10,
                        Size<= 100    ~ 100,
                        Size<= 1000   ~ 1000,
                        Size<= 10000  ~ 10000,
                        Size<= 100000 ~ 100000,
                        Size > 100000 ~ 1000000)) %>% filter(!LogBin == 5) %>% group_by(Species,Condition,TimePoint)%>% 
  mutate(TotalBiomass=sum(Size),TotalFrequency=n()) %>% ungroup() %>% group_by(Species,Condition,TimePoint, LogBin)%>%
  mutate(BinBiomass = sum(Size), BinFrequency = n()) %>% ungroup() %>%
  mutate(NormalizedFrequency = BinFrequency/TotalFrequency*100, NormalizedBiomass = BinBiomass/TotalBiomass*100)

##Summary df
aggsHistCondSum<-aggsHistCond %>% group_by(Species,Condition,TimePoint, Replicate, LogBin,NormalizedFrequency,NormalizedBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Condition,TimePoint, Replicate) %>% mutate(checkSumFreq =sum(NormalizedFrequency), checkSumBiomass = sum(NormalizedBiomass))

#now plot it
#normalized frequency

PlotHistSum(aggsHistRepSum,aggsHistCondSum,"NormalizedFrequency", "Normalized Frequency aggregates only")
PlotHistSum(aggsHistRepSum,aggsHistCondSum,"NormalizedBiomass","Normalized Biomass aggregates only")
PlotHistRepBioTrend(aggsHistRepSum, "Pa")
PlotHistRepBioTrend(aggsHistRepSum, "Sa")

#####
#Planktonic vs aggregates
#####
#Add agregation value to the dataframe
##Normalize using replicates
HistReplicate<-HistReplicate %>%  mutate(Aggregation = case_when(LogBin == 5 ~"Planktonic",LogBin>5 ~ "Aggregate")) %>%
  group_by(Species,Condition,TimePoint, Replicate, Aggregation)%>% 
  mutate(AgPlBiomass = sum(Size), AgPlFreq = n()) %>% ungroup() %>%
  mutate(AgPlNormFrequency = AgPlFreq/TotalFrequency*100, AgPlNormBiomass = AgPlBiomass/TotalBiomass*100)
#Collapse to only values per replicate
plankAggHistRep<-HistReplicate %>% group_by(Species,Condition,TimePoint, Replicate, Aggregation,AgPlNormFrequency,AgPlNormBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Condition,TimePoint, Replicate) %>% mutate(checkAggFreq =sum(AgPlNormFrequency), checkAggBiomass = sum(AgPlNormBiomass))

##Normalize using Condition
HistCondition<-HistCondition %>%  mutate(Aggregation = case_when(LogBin == 5 ~"Planktonic",LogBin>5 ~ "Aggregate")) %>%
  group_by(Species,Condition,TimePoint, Aggregation)%>% 
  mutate(AgPlBiomass = sum(Size), AgPlFreq = n()) %>% ungroup() %>%
  mutate(AgPlNormFrequency = AgPlFreq/TotalFrequency*100, AgPlNormBiomass = AgPlBiomass/TotalBiomass*100)
#Collapse to only values per replicate
plankAggHistCond<-HistCondition %>% group_by(Species,Condition,TimePoint, Aggregation,AgPlNormFrequency,AgPlNormBiomass) %>% summarize() %>%  unique()%>%ungroup() %>%  group_by(Species,Condition,TimePoint) %>% mutate(checkAggFreq =sum(AgPlNormFrequency), checkAggBiomass = sum(AgPlNormBiomass))

#Plot Frequency
ggplot()+
  geom_jitter(data = plankAggHistRep,aes(x=as.factor(Aggregation),y=AgPlNormFrequency,  color =Species, ),size=3, height = 0, width = .2, shape = 1)+ 
  geom_point(data = plankAggHistCond,aes(x=as.factor(Aggregation),y=AgPlNormFrequency,  color =Species,group = Species),size=4, shape = 16, position = position_dodge(width = .3) )+
  facet_grid(Condition~TimePoint)+
  ggtitle("Normalized Frequency (%) Aggs vs Plank")+
  labs(y = "Normalized Frequency (%)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
  theme_half_open()+
  panel_border() +
  #background_grid(major = "y")+
  theme(plot.title = element_text(hjust = 0.5)) 
#Plot Biomass
ggplot()+
    geom_jitter(data = plankAggHistRep,aes(x=as.factor(Aggregation),y=AgPlNormBiomass,  color =Condition ),size=2, height = 0, width = .2, shape = 1)+
  geom_jitter(data = plankAggHistCond,aes(x=as.factor(Aggregation),y=AgPlNormBiomass,  color =Condition,group = Species),size=5, shape = 16,height = 0, width = .2) +
    facet_grid(Species~TimePoint)+
  ggtitle("Normalized Biomass (%) Aggs vs Plank")+
    labs(y = "Normalized Biomass (%)",x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+  scale_color_manual( values = c( "red","blue","green", "gray"),labels = c("Sa Mono", "phz co", "pqsL co", "wt co"))+
    theme_cowplot()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5)) 
#####
```
